Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-05-03 scripts/01_quality_control_normalization.Rmd
Switch bootstrapping proportion

@@

```{r reading_targets, results="hide", fig.width=8, fig.height=4}
# Read in the data using limma.
targets = limma::readTargets()
RG = limma::read.maimages(
  targets, source="agilent",
  path=data_dir,
  other.columns="gIsWellAboveBG",
  green.only=TRUE)

# Preform background correction using norm-exponential strategy and normalize
# across samples using quantile normalization.
RG = limma::backgroundCorrect(RG, method="normexp")
RG.q = limma::normalizeBetweenArrays(RG, method="quantile")
```

>>>>

Given the source and a `Targets.txt` structured as follows, microarray can be loaded thanks to the limma library.

```
FileName
GSM1557140_AR0313_043raw.txt.gz
GSM1557141_AR0313_044raw.txt.gz
GSM1557142_AR0313_045raw.txt.gz
GSM1557143_AR0313_055raw.txt.gz
GSM1557144_AR0313_056raw.txt.gz
GSM1557145_AR0313_057raw.txt.gz
GSM1557146_AR0313_058raw.txt.gz
GSM1557147_AR0313_059raw.txt.gz
```

```{r}
targets = limma::readTargets()
RG = limma::read.maimages(
  targets, source="agilent",
  path=data_dir,
  other.columns="gIsWellAboveBG",
  green.only=TRUE)

@@

```{r reading_targets, results="hide", fig.width=8, fig.height=4}
# Perform background correction using norm-exponential strategy and normalize
# across samples using quantile normalization.
RG = limma::backgroundCorrect(RG, method="normexp")
RG.q = limma::normalizeBetweenArrays(RG, method="quantile")
```

### 2019-05-03 scripts/03_clustering.Rmd
Switch bootstrapping proportion

@@

```{r echo="FALSE"}
library(knitr)
knitr::include_graphics("images/clustering_CDF_consensus.png")
```

@@

```{r echo="FALSE"}
library(knitr)
knitr::include_graphics("images/clustering_CDF_consensus.png")
```

>>>>

To perform such analysis, the first step is run the clustering several times
on a resampled dataset--either using bootstrap or subsampling.

Using the bootstrapping strategy:
```{r}
n_genes = dim(y)[1]
indices = sample(1:dim(y)[1], n_genes, replace=TRUE)

bootstrapped_y = y[indices, ]
```

Using the subsampling strategy, keeping 80% of the genes:
```{r}
subsample_proportion = 0.8
indices = sample(1:dim(y)[1], n_genes * subsample_proportion, replace=TRUE)
subsampled_y = y[indices, ]
```

@@

```{r echo=FALSE}
library(knitr)
knitr::include_graphics("images/clustering_CDF_consensus.png")
```

@@

```{r echo=FALSE}
library(knitr)
knitr::include_graphics("images/clustering_AUC_consensus.png")
```

```{r echo=FALSE}
library(knitr)
knitr::include_graphics("images/clustering_delta_AUC_consensus.png")
```

### 2019-05-03 scripts/04_downstream_analysis.Rmd
Switch bootstrapping proportion

```{r results="hide"}
library(biomaRt)
ensembl = useMart("ensembl")
ensembl = useDataset("mmusculus_gene_ensembl", mart=ensembl)
```

@@

# convert gene names
genes = getBM(attributes=c("ensembl_gene_id", "entrezgene"),
		filters="refseq_mrna", values=genes,
		mart=ensembl)["entrezgene"]
genes = as.vector(unlist(genes))
pathways = KEGGprofile::find_enriched_pathway(
    genes, species="mmu",
    download_latest=TRUE)$stastic

@@

```{r go_to_gene_mapping, results="hide", message=FALSE}
# FIXME move this to the package
source("GO_terms_analysis.R")
genes = getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

```{r go_term_enrichment, results="hide", message=FALSE}
scores = as.numeric(labels == cluster)
names(scores) = gene_names
go_terms_enriched = find_enriched_go_terms(
    scores,
    gene_id_go_mapping, ontology="BP")
```

>>>>

```{r results="hide"}
library(biomaRt)
ensembl = biomaRt::useMart("ensembl")
ensembl = biomaRt::useDataset("mmusculus_gene_ensembl", mart=ensembl)
```

@@

# convert gene names
genes = biomaRt::getBM(attributes=c("ensembl_gene_id", "entrezgene"),
		filters="refseq_mrna", values=genes,
		mart=ensembl)["entrezgene"]
genes = as.vector(unlist(genes))
pathways = KEGGprofile::find_enriched_pathway(
    genes, species="mmu",
    download_latest=TRUE)$stastic

@@

```{r go_to_gene_mapping, results="hide", message=FALSE}
# FIXME move this to the package
genes = biomaRt::getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

```{r go_term_enrichment, results="hide", message=FALSE}
go_terms_enriched = find_enriched_go_terms(
    scores,
    13,
    gene_id_go_mapping, ontology="BP")
```
